Switch equivalence and weak prime domains for fusions

### 2023-10-26 fusione.tex
cose

\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$. Then the following are true: 
	\begin{enumerate}
		\item suppose that $(a_1,a_2)$ and $(e_0,e_1)$ are independence pairs witnessing  $\dder{D}_1\updownarrow_! \dder{D}_2$ and $\dder{D}_0\updownarrow_! S_{a_1,a_2}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{e_0,e_1}(\dder{D}_0)\updownarrow_!S_{a_2,a_2}(\dder{D}_1)$;
		\item 
	\end{enumerate}
\end{corollary}
\begin{proof}
	\begin{enumerate}
		\item Let $(i_1,i_2)$ be the unique independence pair between $\dder{D}_0$ and $\dder{D}_1$.  By tameness and \Cref{lem:iig1} we know that $S_{e_0,e_1}(\dder{D}_0)\updownarrow S_{a_1,a_2}(\dder{D}_1)$. Let $(\alpha_1, \alpha_2)$ be the independence pair constructed in the proof of \Cref{lem:iig1}. Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$. Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$. Let $\sigma:[0,2]\to [0,2]$ be the cycle $(0,1,2)$. By \Cref{lem:consperm} we know that $\sigma$ is a consistente permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$. In particular, we have
		\begin{align*}
			\iota_{\der{E}, G_0}\circ f_0\circ  i_1 &=\xi_\sigma \circ 	\iota_{\der{D}, G_0}\circ f_0\circ  i_1 \\&= \xi_\sigma \circ 	\iota_{\der{D}, D_0}\circ  i_1\\ &= \xi_\sigma \circ \iota_{\der{D}, G_1} \circ g_0\circ  i_1 \\&=\xi_\sigma \circ \iota_{\der{D}, G_1}\circ m_1\\ &=  \iota_{\der{E}, G'_2}\circ y_1\circ b_1\\&= \iota_{\der{E}, G'_2}\circ z'_1\circ \beta_2\\&= \iota_{\der{E}, Q_5}\circ \beta_2 
		\end{align*}
		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2:L_1\to P_3$ fitting in the diagram below
		\[\xymatrix{L_1 \\& P_3 & Q_5\\
		&D_0& \tpro{E}}\]
		If we further compute, we get
		\begin{align*}
			y_1\circ u_1\circ \beta'_2\\&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
		\end{align*}
		Thus $(u_1\circ \beta'_2, b_2)$ is an independence pair between $S_{a_1, a_2}(\der{D}_2)$ and $S_{a_1, a_2}(\der{D}_1)$ therefore, by hypothesis $u_1\circ \beta'_2=b_1$. But this implies that $\beta'_2$ and $\alpha'_2$ are equal, giving us the thesis.

\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}

>>>>

\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$. Then the following are true: 
	\begin{enumerate}
		\item suppose that $(a_1,a_2)$ and $(e_0,e_1)$ are independence pairs witnessing  $\dder{D}_1\updownarrow_! \dder{D}_2$ and $\dder{D}_0\updownarrow_! S_{a_1,a_2}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{e_0,e_1}(\dder{D}_0)\updownarrow_!S_{a_2,a_2}(\dder{D}_1)$;
		\item 
	\end{enumerate}
\end{corollary}

\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
\begin{proof}
	\begin{enumerate}
		\item Let $(i_1,i_2)$ be the unique independence pair between $\dder{D}_0$ and $\dder{D}_1$.  By tameness and \Cref{lem:iig1} we know that $S_{e_0,e_1}(\dder{D}_0)\updownarrow S_{a_1,a_2}(\dder{D}_1)$. Let $(\alpha_1, \alpha_2)$ be the independence pair constructed in the proof of \Cref{lem:iig1}. Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$. Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$. Let $\sigma:[0,2]\to [0,2]$ be the cycle $(0,1,2)$. By \Cref{lem:consperm} we know that $\sigma$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$. In particular, we have
		\begin{align*}
			\iota_{\der{E}, G_0}\circ f_0\circ  i_1 &=\xi_\sigma \circ 	\iota_{\der{D}, G_0}\circ f_0\circ  i_1 \\&= \xi_\sigma \circ 	\iota_{\der{D}, D_0}\circ  i_1\\ &= \xi_\sigma \circ \iota_{\der{D}, G_1} \circ g_0\circ  i_1 \\&=\xi_\sigma \circ \iota_{\der{D}, G_1}\circ m_1\\ &=  \iota_{\der{E}, G'_2}\circ y_1\circ b_1\\&= \iota_{\der{E}, G'_2}\circ z'_1\circ \beta_2\\&= \iota_{\der{E}, Q_5}\circ \beta_2 
		\end{align*}
		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2:L_1\to P_3$ fitting in the diagram below
		\[\xymatrix@C=30pt{L_1  \ar@/^.3cm/[drr]^{\beta_2} \ar@/_.3cm/[ddr]_{i_1}\ar@{.>}[dr]^{\beta'_2}\\& P_3 \ar[r]^{n_1}  \ar[d]_{u_0}& Q_5 \ar[d]^{\iota_{\dder{E}, Q_5}}\\
		&D_0 \ar[r]_{\iota_{\dder{E}, G_0}}& \tpro{E}}\]
		If we further compute, we get
		\begin{align*}
			y_1\circ u_1\circ \beta'_2&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
		\end{align*}
		Thus $(u_1\circ \beta'_2, b_2)$ is an independence pair between $S_{a_1, a_2}(\der{D}_2)$ and $S_{a_1, a_2}(\der{D}_1)$ therefore, by hypothesis $u_1\circ \beta'_2=b_1$. But this implies that $\beta'_2$ and $\alpha'_2$ are equal, giving us the thesis.

\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
